---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = FALSE,
  warning = FALSE,
  message = TRUE,
  tidy = FALSE,
  fig.align='center',
  comment = "#>",
  fig.path = "man/figures/README-",
  R.options = list(width = 200)
)
```


# augmentCongress
A package to extract named members of the U.S. Congress in messy text with typos and inconsistent name formats

Install this package with 
```
devtools::install_github("judgelord/augmentCongress")

library(augmentCongress)
```

Currently, functions are in two scripts: 
```{r, message=FALSE}
# name matching function 
source(here::here("R", "nameMethods.R"))

# common typos and known permutations and nicknames 
source(here::here("R", "MemberNameTypos.R"))
```

## Data

This package relies on a dataframe of permutations of the names of members of Congress. This dataframe builds on the basic structure of voteview.com data, especially the `bioname` field. From this and other corrections, it constructs a regular expression search `pattern` and conditions under which this pattern should yield a match (e.g. when that pattern has a unique match to a member of Congress in a given Congress). `pattern` differs from Congress to Congress because some member move from the House to the Senate and because members with similar names join or leave Congress.

Before searching the text, several functions clean it and "fix" common human typos and OCR errors that frustrate matching. Some of these corrections are currently supplied by `MemberNameTypos.R`. In future versions, `typos` will be supplied as a dataframe and all types of corrections (cleaning, typos, OCR erros) will be optional. 

```{r}
data("members")

members[c("chamber", "congress", "bioname", "pattern")] 
```

## Basic Usage

There are two basic functions

1. `extractMemberName()` returns a list of the names of members of Congress in a supplied vector of text 
2. `augmentCongress()` augments a dataframe that includes at least one unique identifier to include a suite of other common identifiers

For example, we can use `extractMemberName()` to detect the names of members of Congress in the text of the Congressional Record. Let's start with text of the Congressional Record from 3/1/2007, scraped and parsed using methods described [here](https://github.com/judgelord/cr). 

```{r, eval = FALSE, include= FALSE}
# clean up example data from cr repo
cr2007_03_01 %<>% 
  select(date, speaker, header, url, url_txt) %>% 
  #filter(!str_detect(chamber, "Ext")) %>%
  filter(!str_detect(speaker, "^NA$"))

save(cr2007_03_01, file = here::here("data", "cr2007_03_01.rda"))
```

```{r}
data("cr2007_03_01")

cr2007_03_01

head(cr2007_03_01$url)

head(cr2007_03_01$speaker)
```


This is an extremely simple example because the text strings containing the names of the members of Congress (`speaker`) are short and do not contain much other text. However, `extractMemberName()` is also capable of searching longer and much messier texts, including text where names are not consistently formatted or where they contain common typos introduced by humans or common OCR errors. Indeed, these functions were developed to identify members of Congress in ugly text data like [this](https://judgelord.github.io/corr/corr_pres.html#22). 

To better match member names, this function currently requires either

- a column "congress" (this can be created from a date) or 
- a vector of congresses to limit the search to (`congresses`)

### `extractMemberName()`

```{r}
cr2007_03_01$congress <- 110

# extract legislator names and match to voteview ICPSR numbers
cr <- extractMemberName(data = cr2007_03_01, 
                        col_name = "speaker", # The text strings to search
                        congresses = 110, # This argument is not required in this case because the data contain a "congress" column
                        members = members)

cr
```

In this example, all observations are in the 110th Congress, so we only search for members who served in the 110th. Because each row's `speaker` text contains only one member in this case, `data_row_id` and `match_id` are the same. Where multiple members are detected, there may be multiple matches per `data_row_id`.

###  `augmentCongress()`

Because `extractMemberName` links each detected name to ICPSR IDs from voteview.com, we already have some information, like party (`party_name`), state, district, and ideology scores (`nominate.dim1`) for each match in the text of the Congressional Record. 


```{r}
full_join(cr, members) |> select(data_row_id, match_id, bioname, icpsr, congress, state, district_code, party_name, nominate.dim1, url)
```

The function `cr_augmentCongress` is not not yet built, but it will simply join in other datasets on IDs like ICPSR numbers.

```
# add other common unique identifiers
cr_augmented <- augmentCongress(cr)
```
